Devphotodraw_main_anlayses

### 2023-05-02 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
fix typo

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = conditionf)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~who)

@@

>>>>

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~who)

@@

##
```{r}
